---
title: "R Notebook"
output: html_notebook
---



```{r}
dataset_path <- "/Users/zhangxiaoyi/Desktop/StudentPerformanceFactors.csv"  # 替换为实际的数据集文件路径
student_data <- read.csv(dataset_path)
```
```{r}
library(ggplot2)
ggplot(student_data, aes(x = Hours_Studied, y = Exam_Score)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue") +
  labs(title = "score vs study hours", x = "study hours", y = "score")

```
```{r}
library(ggplot2)
ggplot(student_data, aes(x = Attendance, y = Exam_Score)) +
  geom_point() +
  geom_smooth(method = "lm", color = "red") +
  labs(title = "score vs attendance", x = "attendance", y = "score")
```
```{r}
library(ggplot2)
ggplot(student_data, aes(x = Sleep_Hours, y = Exam_Score)) +
  geom_point() +
  geom_smooth(method = "lm", color = "orange") +
  labs(title = "score vs sleep hours", x = "sleep hours", y = "score")

ggplot(student_data, aes(x = Sleep_Hours, y = Exam_Score, fill = Sleep_Hours )) +
  #scale_fill_gradient(low = "lightblue", high = "darkblue") +
  stat_summary(fun = mean, geom = "bar") +
  stat_summary(fun = mean, geom = "text", aes(label = round(..y.., 1)), 
               vjust = -0.5, size = 3, color = "black") +
  labs(title = "score vs sleep hours", x = "sleep hours", y = "score")
```
从这里开始是散点图！
1.family income

```{r}
ggplot(student_data, aes(x = Family_Income, y = Exam_Score ,fill=Family_Income)) +
  scale_fill_brewer(palette = "Set2") +
  stat_summary( fun=mean,geom = "bar") +
  stat_summary(fun = mean, geom = "text", aes(label = round(..y.., 1)), 
               vjust = -0.5, size = 3, color = "black") +
  labs(title = "score vs family income", x = "family income", y = "score")
```
2.parental education level
```{r}
ggplot(student_data, aes(x = Parental_Education_Level, y = Exam_Score ,fill=Parental_Education_Level)) +
  scale_fill_brewer(palette = "Set2") +
  stat_summary( fun=mean,geom = "bar") +
  stat_summary(fun = mean, geom = "text", aes(label = round(..y.., 1)), 
               vjust = -0.5, size = 3, color = "black") +
  labs(title = "score vs parental education level", x = "parental education level", y = "score")
```
3.peer influence
```{r}
ggplot(student_data, aes(x = Peer_Influence, y = Exam_Score ,fill=Peer_Influence)) +
  scale_fill_brewer(palette = "Set2") +
  stat_summary( fun=mean,geom = "bar") +
  stat_summary(fun = mean, geom = "text", aes(label = round(..y.., 1)), 
               vjust = -0.5, size = 3, color = "black") +
  labs(title = "score vs peer influence", x = "peer influence", y = "score")
```
4.distance from home
```{r}

ggplot(student_data, aes(x = Distance_from_Home, y = Exam_Score ,fill=Distance_from_Home)) +
  scale_fill_brewer(palette = "Set2") +
  stat_summary( fun=mean,geom = "bar") +
  stat_summary(fun = mean, geom = "text", aes(label = round(..y.., 1)), 
               vjust = -0.5, size = 3, color = "black") +
  labs(title = "score vs distance from home", x = "distance", y = "score")
```

motivation level
```{r}
ggplot(student_data, aes(x = Motivation_Level, y = Exam_Score ,fill=Motivation_Level)) +
  scale_fill_brewer(palette = "Set2") +
  stat_summary( fun=mean,geom = "bar") +
  stat_summary(fun = mean, geom = "text", aes(label = round(..y.., 1)), 
               vjust = -0.5, size = 3, color = "black") +
  labs(title = "score vs motivation level", x = "motivation level", y = "score")
```
access to resources
```{r}
ggplot(student_data, aes(x = Access_to_Resources, y = Exam_Score ,fill=Access_to_Resources)) +
  scale_fill_brewer(palette = "Set2") +
  stat_summary( fun=mean,geom = "bar") +
  stat_summary(fun = mean, geom = "text", aes(label = round(..y.., 1)), 
               vjust = -0.5, size = 3, color = "black") +
  labs(title = "score vs access to resources", x = "access to resources", y = "score")
```
teacher quality
```{r}
ggplot(student_data, aes(x = Teacher_Quality, y = Exam_Score ,fill=Teacher_Quality)) +
  scale_fill_brewer(palette = "Set2") +
  stat_summary( fun=mean,geom = "bar") +
  stat_summary(fun = mean, geom = "text", aes(label = round(..y.., 1)), 
               vjust = -0.5, size = 3, color = "black") +
  labs(title = "score vs teacher quality", x = "teacher quality", y = "score")
```

physical activity

```{r}

ggplot(student_data, aes(x = Physical_Activity, y = Exam_Score, fill = Physical_Activity )) +
  stat_summary(fun = mean, geom = "bar") +
  stat_summary(fun = mean, geom = "text", aes(label = round(..y.., 1)), 
               vjust = -0.5, size = 3, color = "black") +
  labs(title = "score vs pysical activity", x = "physical activity", y = "score")
```
从这里开始是分面图：
```{r}
ggplot(student_data, aes(x = Hours_Studied, y = Exam_Score)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  facet_wrap(~ Gender) +
  labs(
    title = "score vs study hour(faceted by gender)",
    x = "study hour",
    y = "score"
  ) +
  theme_minimal()
```

```{r}
ggplot(student_data, aes(x = Attendance, y = Exam_Score)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "skyblue") +
  facet_wrap(~ Gender) +
  labs(
    title = "score vs attendance(faceted by gender)",
    x = "attendance",
    y = "score"
  ) +
  theme_minimal()
```
```{r}
ggplot(student_data, aes(x = Sleep_Hours, y = Exam_Score, fill = Gender)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge") +
  stat_summary(fun = mean, geom = "text", aes(label = round(..y.., 1)), 
               position = position_dodge(width = 0.9), vjust = -0.5, size = 3, color = "black") +
  facet_wrap(~ Gender) +
  labs(
    title = "score vs sleep hours(faceted by gender)",
    x = "sleep hours",
    y = "score"
  ) +
  theme_minimal()

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

